\section{Google Cloud Spanner}
\index{Google Spanner}

With exponential increase in the size of data , adaptation of horizontally 
scale databases increases. Most data for business systems was stored in relational
databses earlier. There was a need to bridge this gap between these two database
environments in high performance high availability environment. Cloud Spanner 
bridges this gap. It is cloud based service for globally-distributed database 
This technology combines the benefits of relational database structure 
with non-relational databses that can scale horizontally. This is unique combination 
that allows transactions to be executed with high performance and greater consistency 
Cloud Spanner revolutionizes database administration and management and makes 
application development more efficient~\cite{hid-sp18-523-www-google-spanner}.
It is fully managed, can be easily deployed and comes with out of the box
synchronous and replication functionality~\cite{hid-sp18-523-www-google-spanner}. 
It takes advantages of all critical features of relational database—such 
as schemas, ACID transactions, and SQL queries (ANSI 2011) thus reducing 
the need of high learning curve for developers who are well proficient in 
structured query language. 
Client libraries that can connect to spanner is language independent. 
These libraries can be developed in C sharp, Go, Java, Node.js, PHP, Python, 
and Ruby. Already existing JDBC driver with popular third-party tools can be 
used to connect with spanner~\cite{hid-sp18-523-www-google-spanner}. It is 
purposely built for global transactional consistency.
